Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-22 DGMM2025/paper.tex
Add figure

>>>>

    \begin{figure}
      \begin{center}
        \begin{tabular}{|c||c|c|c|} \hline
          Curvature & II normals & CTriv normals & Our normals \\ \hline \hline
          $\kappa_1$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-II.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-CTriv.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k1-NV.png}\\ \hline
          $\kappa_2$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-II.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-CTriv.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-k2-NV.png}\\ \hline
          $H$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-H-II.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-H-CTriv.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-H-NV.png}\\ \hline
          $G$&
          \includegraphics[width=0.3\textwidth]{pictures/d20-G-II.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-G-CTriv.png}&
          \includegraphics[width=0.3\textwidth]{pictures/d20-G-NV.png}\\ \hline
        \end{tabular}
      \end{center}
      \caption{Estimation of curvatures using Corrected Normal Current
        estimators \cite{} for the shape ``Dice-20'' of Thingi10K
        database at resolution $256^3$. This estimator is
        parameterized by an input normal estimator: first column by
        ``Integral Invariant normals'' (radius $r=4.77$, second column
        by ``Convolved Trivial normals'' (radius $k=3$), third column
        by our presented normal estimator (radius $r=8.5$). Per row are displayed the
        estimated curvatures in order: first and second principal
        curvatures $\kappa_1$ and $\kappa_2$, mean curvature $H$,
        Gaussian curvature $G$. The range of curvature between deep
        blue and deep red is $\lbrack -0.1, 0.1 \rbrack$ with white
        color equal to $0$.}
    \end{figure}
